Boutiques: a flexible framework for automated application integration in computing platforms

### 2017-10-04 paper.tex
Added new applications imported into VIP and 2 comments/questions to Tristan

Until recently, applications were manually integrated in VIP as workflows written 
in the Gwendia\cite{MONT-09} language and managed  with the MOTEUR\cite{GLAT-08} workflow engine. 
As of today, Boutiques is supported through a "Boutiques application importer" tool, which 
parses the JSON file and automatically generates the corresponding application workflow
and the wrapper script that handles, among others, the execution of the command line itself. 
The use of an application workflow allows to (i) iterate on input lists and generate 
parallel tasks, as well as to (ii) concatenate multiple tools. The applications used in 
the MICCAI challenges, for example, were followed by other tool allowing to compute 
challenge-specific metrics. Tool concatenation is currently handeled at the importer 
level based on pre-defined workflow templates.

\todo{Tristan: validate the description above}

@@

A few MRtrix3\footnote{\url{http://www.mrtrix.org/}} tools were also make available in VIP. 
A script developed at Creatis, which combines MRtrix3 and FSL tools, is currently being
imported and tested.

\todo{Tristan: validate the descriptions above}

>>>>

Until recently, applications were manually integrated in VIP as workflows written 
in the Gwendia\cite{MONT-09} language and managed  with the MOTEUR\cite{GLAT-08} workflow engine. 
As of today, Boutiques is supported through a "Boutiques application importer" tool, which 
parses the JSON file and automatically generates the corresponding application workflow
and the wrapper script that handles, among others, the execution of the command line itself. 
The use of an application workflow allows to (i) iterate on input lists and generate 
parallel tasks, as well as to (ii) concatenate multiple tools. The applications used in 
the MICCAI challenges, for example, were followed by other tools allowing to compute 
challenge-specific metrics. Tool concatenation is currently handeled at the importer 
level based on pre-defined workflow templates.

\note{sorina}{@tristan: some info on workflows is available in the paragraph above. Is it OK/enough or do you have other suggestions?}

@@

A few MRtrix3\footnote{\url{http://www.mrtrix.org/}} tools were also made available in VIP, as well as 
a script developed at Creatis, which combines MRtrix3 and FSL tools.

A few other applications from the FLI (France Life Imaging) consortium were also imported in
VIP using Boutiques. One of them is Ginfizz, a FMRI pipeline allowing to execute multiple 
preprocessing steps and basic analyses such as: (i) realignment (motion registration and correction),
(ii) slice timing (temporal interpolation to correct for the delay of acquisition between slices), 
(iii) coregistration (registering functional and structural data), (iv) normalization (registering 
of functional and anatomical data to a match a template that has to be specified), and (iv)
smoothing (spatial filtering to increase Signal to Noise ratio). The use of Docker containers (\url{https://hub.docker.com/r/fliiam/ginfizz} based on \url{https://hub.docker.com/r/miykael/nipype_level2}) 
greatly simplifies its deployment. The animaN4BiasCorrection tool from the Anima  \footnote{\url{https://github.com/Inria-Visages/Anima-Public/wiki}} project was also made available 
in VIP. The import process was straightforward.

\note{sorina}{@tristan: please check if you agree with the descriptions above}
